%-------------------------
% Resume in Latex (Template for Students / Developers)
% Replace all fields written in CAPITAL LETTERS with your details
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\raggedbottom
\raggedright

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% RESUME STARTS HERE
%-------------------------

\begin{document}

%-----------HEADER-----------
\begin{center}
    {\Huge \scshape Your Name} \\ \vspace{2pt}
    \small
    \faPhone\ +91-999999999 ~
    \faEnvelope\ exmaple@gmail.com ~
    \faLinkedin\ \href{https://www.linkedin.com/in/pagalavan-p-713b13204/}{linkedin.com/in/pagalavan-p} ~
    \faCode\ \href{https://leetcode.com/u/pagalavanweb/}{leetcode.com/u/pagalavanweb}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}

\resumeSubHeadingListStart

\resumeItem{

[YOUR ROLE] with [X YEARS] of experience in developing scalable web applications and backend systems.

Strong experience in [MAIN TECHNOLOGIES].

Skilled in building REST APIs, database design, system optimization, and deploying production-ready applications.

}

\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}, itemsep=2pt]

\small{

\item \textbf{Programming Languages:} Python / Java / C++ / JavaScript / SQL

\item \textbf{Frontend Technologies:} HTML5, CSS3, JavaScript, React.js / Angular / Vue

\item \textbf{Backend Frameworks:} FastAPI / Django / Spring Boot / Node.js

\item \textbf{Databases:} MySQL / PostgreSQL / MongoDB / Redis

\item \textbf{DevOps \& Cloud:} Docker / AWS / Linux / Git / CI-CD

\item \textbf{API Development:} REST APIs, JWT Authentication, OAuth, Microservices

\item \textbf{System Design:} Caching, Rate Limiting, Background Jobs, Load Balancing

\item \textbf{Tools:} Postman, GitHub, VS Code, Jira

}

\end{itemize}


%-----------WORK EXPERIENCE-----------
\section{Work Experience}

\resumeSubHeadingListStart


\resumeSubheading
{JOB TITLE – COMPANY NAME}{START DATE -- END DATE}
{LOCATION}{}

\resumeItemListStart

\resumeItem{Developed scalable backend services using [TECHNOLOGIES].}

\resumeItem{Built REST APIs supporting [NUMBER]+ daily users.}

\resumeItem{Optimized database queries and improved system performance by [PERCENTAGE]\%.}

\resumeItem{Collaborated with frontend teams to develop responsive interfaces.}

\resumeItem{Implemented authentication systems such as JWT / OAuth.}

\resumeItemListEnd


\resumeSubheading
{JOB TITLE – COMPANY NAME}{START DATE -- END DATE}
{LOCATION}{}

\resumeItemListStart

\resumeItem{Developed backend modules using [TECHNOLOGY].}

\resumeItem{Designed APIs and database schemas for scalable applications.}

\resumeItem{Improved application performance and reduced response time.}

\resumeItem{Worked in Agile teams to deliver production features.}

\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}

\resumeSubHeadingListStart


\resumeSubheading
{PROJECT NAME}{}
{TECH STACK USED}{}

\resumeItemListStart

\resumeItem{Developed a full-stack application using [TECH STACK].}

\resumeItem{Implemented secure authentication and authorization.}

\resumeItem{Built REST APIs and integrated frontend UI.}

\resumeItem{Optimized performance and implemented caching mechanisms.}

\resumeItemListEnd



\resumeSubheading
{PROJECT NAME}{}
{TECH STACK USED}{}

\resumeItemListStart

\resumeItem{Designed and developed backend services using [TECHNOLOGY].}

\resumeItem{Implemented real-time communication using WebSockets / APIs.}

\resumeItem{Built dashboards and UI components for data visualization.}

\resumeItemListEnd



\resumeSubHeadingListEnd



%-----------PROBLEM SOLVING-----------
\section{Problem Solving}

\resumeSubHeadingListStart

\resumeItem{Solved [NUMBER]+ Data Structures and Algorithms problems on platforms such as LeetCode / HackerRank.}

\resumeItem{Strong understanding of Arrays, Strings, Linked Lists, Recursion, Trees, Graphs, and Dynamic Programming.}

\resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section{Education}

\resumeSubHeadingListStart

\resumeSubheading
{DEGREE NAME}{GRADUATION YEAR}
{COLLEGE / UNIVERSITY NAME}{CGPA / PERCENTAGE}

\resumeSubHeadingListEnd


\end{document}